\LARGE \bf Mean Estimation from One-Bit Measurements

### 2022-05-02 distributed-estimation.tex
example for A2-(ii)

\subsection{Optimal Efficiency}
We begin by making a few restrictions on the collections of the sets $A_i$,
which we believe not unreasonable, but which allow us to develop fundamental
limits for estimation. We require a bit of notation to define the
assumptions. As we work with a location family based on a density $f$
with associated probability distribution $P$ on variables $Z$,
we define
\begin{equation*}
  P_\theta(A) \defeq P(Z - \theta \in A)
\end{equation*}
for $Z$ with density $f$. Whenever $A$ is a collection of disjoint intervals $A = \cup_i [t_i^-, t_i^+]$, we may define
\begin{equation*}
  \dPtheta(A) \defeq \frac{\partial}{\partial \theta} P_\theta(A)
  = \sum_i \left(f(t_i^- - \theta) - f(t_i^+ - \theta)\right),
\end{equation*}
and similarly we define the score
function $\score_\theta(A) \defeq \dPtheta(A) / P_\theta(A)$.
For $B = \indic{X \in A}$, we abuse notation and also write
$\score_\theta(B) = \score_\theta(A)$ and similarly for $\dPtheta$.
With this, we may define the variance of the
scores $\score_\theta(B_i)$ under $P_\theta$ via
\begin{equation}
  \label{eq:precision_general}
  L_n(A_1,\ldots,A_n;\theta) \defeq
  \frac{1}{n} \sum_{i=1}^n \frac{ \dPtheta(A_i)^2}{
    P_\theta(A_i) (1 - P_\theta(A_i))}.
\end{equation}
We then make the following assumption.
\begin{assumption}
  \label{assumption:detection-regions}
  The density and detection regions satisfy
  \begin{enumerate}[(i)]
  \item \label{item:lipschitz-density}
    The density function $f$ of $X_n - \theta$ is Lipschitz continuous.
  \item \label{item:finite-intervals}
    Each set $A_i$ is the finite union of $k_i$ disjoint intervals
    (which may include $\pm \infty$), where
    \begin{equation*}
      \frac{1}{n} \cdot \max_{i \le n} \frac{k_i^3}{P_\theta(A_i)^4
        (1 - P_\theta(A_i))^4} \to 0.
    \end{equation*}
    %% Each set $A_n$ is a finite union of at most $K < \infty$ intervals
    %% (which may include $\pm \infty$), and
    %% $0 < \inf_n P_\theta(A_n) \le \sup_n P_\theta(A_n) < 1$.
  \item \label{item:limit-variance}
    The limit
    \begin{equation}
      \label{eqn:LAN-limit}
      \kappa(\theta) \defeq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
    \end{equation}
    exists and is finite.
  \end{enumerate}
\end{assumption}

Under this assumption, we have the following theorem, which provides
a local asymptotic minimax lower bound on the efficiency of
\emph{any} non-adaptive estimator.
\begin{theorem}
  \label{theorem:non-adaptive-minimax}
  Let Assumption~\ref{assumption:detection-regions} hold, and
  let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from
  observations $B_i = \indic{X_i \in A_i}$.
  Then for $Z \sim \normal(0, 1)$ and any
  symmetric and quasi-convex function $L$,
  \begin{align*}
    & \liminf_{c \to \infty} \liminf_{n \to \infty}
    \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}
    \E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right] \\
    & \qquad \qquad \qquad \qquad \geq
    \E\left[ L (Z/\sqrt{\kappa(\theta)}) \right].
  \end{align*}
\end{theorem}
\noindent
See Appendix~\ref{sec:proof-non-adaptive-minimax} for a proof.

>>>>

\subsection{Optimal Efficiency}
We begin by making a few restrictions on the collections of the sets $A_i$,
which we believe not unreasonable, but which allow us to develop fundamental
limits for estimation. We require a bit of notation to define the
assumptions. As we work with a location family based on a density $f$
with associated probability distribution $P$ on variables $Z$,
we define
\begin{equation*}
  P_\theta(A) \defeq P(Z - \theta \in A)
\end{equation*}
for $Z$ with density $f$. Whenever $A$ is a collection of disjoint intervals $A = \cup_i [t_i^-, t_i^+]$, we may define
\begin{equation*}
  \dPtheta(A) \defeq \frac{\partial}{\partial \theta} P_\theta(A)
  = \sum_i \left(f(t_i^- - \theta) - f(t_i^+ - \theta)\right),
\end{equation*}
and similarly we define the score
function $\score_\theta(A) \defeq \dPtheta(A) / P_\theta(A)$.
For $B = \indic{X \in A}$, we abuse notation and also write
$\score_\theta(B) = \score_\theta(A)$ and similarly for $\dPtheta$.
With this, we may define the variance of the
scores $\score_\theta(B_i)$ under $P_\theta$ via
\begin{equation}
  \label{eq:precision_general}
  L_n(A_1,\ldots,A_n;\theta) \defeq
  \frac{1}{n} \sum_{i=1}^n \frac{ \dPtheta(A_i)^2}{
    P_\theta(A_i) (1 - P_\theta(A_i))}.
\end{equation}
We then make the following assumption.
\begin{assumption}
  \label{assumption:detection-regions}
  The density and detection regions satisfy
  \begin{enumerate}[(i)]
  \item \label{item:lipschitz-density}
    The density function $f$ of $X_n - \theta$ is Lipschitz continuous.
  \item \label{item:finite-intervals}
    Each set $A_i$ is the finite union of $k_i$ disjoint intervals
    (which may include $\pm \infty$), where
    \begin{equation*}
      \frac{1}{n} \cdot \max_{i \le n} \frac{k_i^3}{P_\theta(A_i)^4
        (1 - P_\theta(A_i))^4} \to 0.
    \end{equation*}
  \item \label{item:limit-variance}
    The limit
    \begin{equation}
      \label{eqn:LAN-limit}
      \kappa(\theta) \defeq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
    \end{equation}
    exists and is finite.
  \end{enumerate}
\end{assumption}
Roughly speaking, \eqref{item:finite-intervals} above holds whenever the intervals consisting each $A_i$ are appropriately seperated. For example, it applies when each set $A_i$ is a half-bounded interval $(t_i,\infty)$ with $\min\{P_\theta((t_i,\infty)), P_\theta((-\infty,t_i])\} = \omega(1/n)$ as we dicscuss in more detail below. More generally, suppose that $A_i = \cup_{j=1}^{k_i}[t_{i,j}^-, t_{i,j}^+]$ and let 
\begin{align*}
c_n^+ & =  \min_{i \le n} \min_{j \leq k_i}  F(t^+_{i,j} - \theta) - F(t^-_{i,j}- \theta) \\
c_n^- & = \min_{i \le n} \min_{j \leq k_i}  F(t^-_{i,j+1}- \theta)  - F(t^+_{i,j}- \theta),
\end{align*}
with $t^-_{i,k_i+1} = \infty$. Then Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals} holds whenever $\max_{i \le n} k_i^3 (c_n^- c_n^+)^4 = o(n)$.

Under Assumption~\ref{assumption:detection-regions}, we have the following theorem, which provides
a local asymptotic minimax lower bound on the efficiency of
\emph{any} non-adaptive estimator.
\begin{theorem}
  \label{theorem:non-adaptive-minimax}
  Let Assumption~\ref{assumption:detection-regions} hold, and
  let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from
  observations $B_i = \indic{X_i \in A_i}$.
  Then for $Z \sim \normal(0, 1)$ and any
  symmetric and quasi-convex function $L$,
  \begin{align*}
    & \liminf_{c \to \infty} \liminf_{n \to \infty}
    \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}
    \E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right] \\
    & \qquad \qquad \qquad \qquad \geq
    \E\left[ L (Z/\sqrt{\kappa(\theta)}) \right].
  \end{align*}
\end{theorem}
\noindent
See Appendix~\ref{sec:proof-non-adaptive-minimax} for a proof.
